\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans

### 2018-02-01 trips.tex
Added changes proposed in blue and simplified enumerations to save space

\begin{align}
n &\ge 1 , \label{e.trip.constraints.1} \\
\tau_{(i)} &< jt^{k}_{u(i)} < \Tau_{(i)} \ , \ \forall i \in jt^{k}_{u(i)} \label{e.trip.constraints.2},
\end{align}
{\color{blue}where $\tau$ is ... and $T_{(i)}$ ...}

@@

{\color{blue}where $c_i^k$ is ..., }

@@

Number plate recognition cameras have accuracy rates of 99.9\% or higher. If we consider that on average 1 to 10 out of 10000 scans are misclassified number-plates then approximately 200 to 2000 scans everyday are incorrect. We categorise the errors made by ANPR cameras into two types:
\begin{enumerate}
  \item a passing vehicle is not detected by the camera;
  \item a different vehicle is detected instead.
\end{enumerate}
In the first case, there is no observed data. The corresponding trip sequence for the affected vehicle will be missing a sighting but we will have no indication of this. It should be noted that this could also happen in the case where a vehicle does not take the `normal' route and pass this intermediary camera. For the second case, there is a recorded sighting, but this will be assigned to the incorrect vehicle. Even though, the camera provides a value of \emph{confidence} which helps in diagnosing incorrect scans, errors still occur for high values of confidence. Even so, in this work we do not present a complex solution for this issue. Methods to detect and address these two types of errors need to be designed and implemented in the future.

>>>>

\begin{align}
n &\ge 1 , \label{e.trip.constraints.1} \\
\tau_{(i)} &< jt^{k}_{u(i)} < \Tau_{(i)} \ , \ \forall i \in jt^{k}_{u(i)} \label{e.trip.constraints.2},
\end{align}
where $\tau_{(i)}$ and $\Tau_{(i)}$ are the lower and upper bound of the $i_{th}$ element of the journey time sequence.

@@

where $c_i^k$ and $t_i^k$ are the camera and timestamp of the $i_{th}$ sighting of vehicle $k$.

@@

Number plate recognition cameras have accuracy rates of 99.9\% or higher. If we consider that on average 1 to 10 out of 10000 scans are misclassified number-plates then approximately 200 to 2000 scans everyday are incorrect. We categorise the errors made by ANPR cameras into two types:
\begin{enumerate*}[label=(\roman*)]
  \item a passing vehicle is not detected by the camera;
  \item a different vehicle is detected instead.
\end{enumerate*}
In the first case, there is no observed data. The corresponding trip sequence for the affected vehicle will be missing a sighting but we will have no indication of this. It should be noted that this could also happen in the case where a vehicle does not take the `normal' route and pass this intermediary camera. For the second case, there is a recorded sighting, but this will be assigned to the incorrect vehicle. Even though, the camera provides a value of \emph{confidence} which helps in diagnosing incorrect scans, errors still occur for high values of confidence. Even so, in this work we do not present a complex solution for this issue. Methods to detect and address these two types of errors need to be designed and implemented in the future.
